---
title: "Final Exam Part 2"
author: "Cassie Giovannetti"
date: "3/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE)
library(tidyverse)
library(here)
```


```{r}
nptrails <- read.csv(here("national_park_trails.csv"))
```

Question 1.1 [10 points]
Which National Park contains the most trails with a 5-star average rating?

```{r}
nptrails %>%
  filter(avg_rating == 5.0) %>%
  select(area_name, avg_rating) %>%
  count(area_name) %>%
  slice_max(n)
```


Question 1.2 [10 points]
What are the three longest trails in this dataset, in miles?

```{r}
nptrails %>%
  select(name, length) %>%
  mutate(miles = length*0.000621371) %>%
  arrange(desc(length)) %>%
  slice_head(n = 3)
```

Question 1.3 [10 points]
What is the most popular trail in each National Park?

```{r}
nptrails %>%
  select(name, area_name, popularity) %>%
  arrange(desc(popularity)) %>%
  group_by(area_name) %>%
  summarise(Most_Popular_Trail = max(popularity))
```


Question 1.4 [10 points]
How many National Parks contain the word “Canyon” somewhere in their name?

```{r}
nptrails %>%
  select(area_name) %>%
  filter(str_detect(area_name, "Canyon")) %>%
  count(area_name)
```


Question 1.5 [20 points]
What are the five common words used in trail names?
Do not include words that mean “trail”, like “trail”, “route”, “path”, “loop”.
Do not include connector words like “to”, “and”, “with”, “via”, etc.

my idea for this question:
nptrails <- nptrails %>%
  select(name) %>%
  mutate(Split <- str_split(name, " "))

output <- vector("character", ncol = 3)
for (i in seq_along(nptrails$Split)) {
    output[[i]] <- nptrails$Split[[i]]
  }
  


`


Question 1.6 [20 points]
Write a function that takes two required inputs:

the dataset
the name of a National Park
Your function should also accept the following optional arguments:

A minimum trail length (in miles)
A maximum trail length (in miles)
A minimum trail rating
The type of trail (out and back, loop, or point to point)
The function should return all the trails that fit the supplied criteria. You may assume that the variable names of the inputted dataset match the np_trails dataset.

```{r}
nptrails <- nptrails %>%
  mutate(miles = length*0.000621371) 
```


```{r}
recommend_trails <- function(data, area_name, min_len_mi = 1, max_len_mi = 300, min_rating = 2.3, type = "loop") {
  min_length = min(data$miles)
  max_length = max(data$miles)
  min_rate = min(data$avg_rating)
  route_type = data$route_type
  
  if (area_name == data$area_name) {
      if (min_len_mi == min_length){
        trails == (data$name)
          return(trails)
      }
      if (max_len_mi == max_length){
          trails == (data$name)
          return(trails)
      }

      if (min_rating == min_rate){
          trails == (data$name)
          return(trails)
      }
      if (type == route_type){
         trails == (data$name)
        return(trails)
      }

    }

}
  
```


  }

Include the following code in your response to verify that your function works:

```{r}
nptrails %>%
  recommend_trails("Yellowstone National Park", 
                   min_len_mi = 10, 
                   min_rating = 4, 
                   type = "loop")
```
```{r}
nptrails %>%
  recommend_trails("Yellowstone National Park", 
                   min_len_mi = 10, 
                   min_rating = 4, 
                   type = "loop")
```


Question 1.7 [20 points]
Use your function from Question 1.6, along with a map() or apply() function to recommend to me all the trails that are:

20-30 miles long (good for a two day backpacking trip!)

Rated at least a 4.5

Loop trails (I don’t like to retrace my steps)

In one of the parks closest to SLO:

* Sequoia National Park
* Joshua Tree National Park
* Lassen Volcanic National Park
* Kings Canyon National Park
* Pinnacles National Park
* Death Valley National Park
